---
title: "Lab 5"
author: "Evie Vermeer"
date: "10/25/2021"
output: 
  html_document: 
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, echo= TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the t.test() function to calculate confidence intervals

### Example 1

Create a single mock sample containing a number of values, then learn to use t.test() to return confidence intervals, and learn about in-line code referencing so our tesxt becomes more reproducible, too. 

```{r}
# Create a mock sample - using c() to create a vector

otter_lengths <- c(30,28,22,25,32,26,54,45,42)

# Find the confidence interval from our sample:

otter_ci <- t.test(otter_lengths)

# Find the standard deviation

otter_sd <- sd(otter_lengths)

n_otter <- length(otter_lengths)
```

95% confidence interval means that if you took multiple samples from this population, you'd expect 95% of those sample confidence intervals to contain the true population mean. 

Mean otter length is 33.8 ($\pm$ 10.8, n=9) inches with a 95% confidence interval of [25.5,42.1] inches. 

#### Now, using in-line referencing 
Mean otter length is `r round(otter_ci$estimate,1)` inches, with a 95% confidence interval of [`r round(otter_ci$conf.int[1],1)`,`r round(otter_ci$conf.int[2],1)`] inches.

## Part 2: Two-sample t-tests

### Example 1

Make two mock samples, ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the same mean. 

```{r}
# Make my mock samples

oak_trees <- c(45,39,44,60,43)

pine_trees <- c(85,72,76,77,105,69)

# Two-sample t-test
tree_t <- t.test(oak_trees,pine_trees)

# Null hypothesis means heights are the same
#i.e. : Trees are drawn from populations with the same mean height



```

 P - value of xxx means there is a XXX % chance that if these are samples from populations with the same mean, the samples will be at least this far apart. In this case, the low p-value means there is a very low chance that these samples come from populations with the same mean. 


The mean heights of oak and pine trees were (46.2 +- (sd)) and (80.7 +- (sd)), respectively, and the different was not significant (t(`r round(tree_t$parameter,1)`) = `r round(tree_t$statistic,1)`, p = `r round(tree_t$p.value,1)`)

"t(df) = t-statistic, p = p-value"

*AVOID* p=0 
When things get really small, use P < 0.001


## Part 3: Another t-test with car data

### Take a look at the data

```{r}
compact_suv <- mpg %>% 
  filter(class %in% c("compact","suv"))
# Check for remaining levels 

unique(compact_suv$class)

```


Create a histogram of city (cty) gas mileage, faceted by class, starting from compact_suv

```{r}
ggplot(compact_suv,aes(x=cty))+
geom_histogram(bins = 12, fill="forestgreen") + 
  theme_bw()+
  facet_wrap(~class)


ggplot(data = compact_suv, aes(sample = cty))+
  geom_qq()+
  facet_wrap(~class)

```

Find some summary statistics for each group
 
```{r}
car_stats <- compact_suv %>% 
  group_by(class) %>% 
  summarize(
    mean_city = round(mean(cty),2),
    sd_city = round(sd(cty),2),
    sample_size = n()         )
  
```
 
The t.test function REALLY wants vectors of things. 

```{r}
compact_sample <- compact_suv %>% 
  filter(class == "compact") %>% 
  pull(cty)

# Your turn, do the same thing to get a vector of city gas mileages for SUVS

suv_sample <- compact_suv %>% 
  filter(class == "suv") %>% 
  pull(cty)
```

H0: Mean city gas mileages for SUVS and compact cars are the same

```{r}
t.test(compact_sample,suv_sample)
```

There is a significant difference in mean city gas mileage for SUVs and compact cars. t(df) = t-statistic, p <0.001.





