---
title: "Lab 5"
author: "Evie Vermeer"
date: "10/25/2021"
output: 
  html_document: 
    toc: yes
    code_folding: hide
---

```{r setup, include=TRUE, echo= TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals

In this section, we'll use the t.test() function to calculate confidence intervals

### Example 1

Create a single mock sample containing a number of values, then learn to use t.test() to return confidence intervals, and learn about in-line code referencing so our tesxt becomes more reproducible, too. 

```{r}
# Create a mock sample - using c() to create a vector

otter_lengths <- c(30,28,22,25,32,26,54,45,42)

# Find the confidence interval from our sample:

otter_ci <- t.test(otter_lengths)

# Find the standard deviation

otter_sd <- sd(otter_lengths)
```

95% confidence interval means that if you took multiple samples from this population, you'd expect 95% of those sample confidence intervals to contain the true population mean. 

Mean otter length is 33.8 ($\pm$ 10.8, n=9) inches with a 95% confidence interval of [25.5,42.1] inches. 

#### Now, using in-line referencing 
Mean otter length is `r round(otter_ci$estimate,1)` inches




